
 \subsection{Applications and Data}
We envision several applications and scenarios where faithful generation might
be useful. The first is for data-to-text generation tasks. We plan on 
training the structured data model on at least two data-to-text tasks. 
The first is a biography generation task using biographical Wikipedia
entries and structured data extracted from the corresponding Wikipedia page's
info box \citep{lebret2016neural}. The second data-to-text task is a 
restaurant description generation task, where the structured data consists
of data about restaurants (types of food offered, location, etc.) 
\citep{novikova2017e2e}.
For the text-to-text scenarios, we plan to perform faithful summary generation
first using the TL;DR dataset \citep{volske2017tl} which contains over 2 
million
Reddit comments with summarizations. Since the comments being summarized
are shorted than most news articles, we think this will be a more tractible
starting point for validating the utility of the cloze task.
Following this, we would like to apply this technique to
the CNN/DailyMail, NYT, and Newsroom datasets 
\citep{hermann2015teaching,sandhaus2008new,grusky2018newsroom}.


We would also like to explore ways in which faithful generation could 
be applied to understanding and controlling for bias in machine learning
\citep{bolukbasi2016man}. By modifying the faithful generation objective
function to reward only uncertainty for missing data fields, we could 
encourage the generator to produce utterances that are decorrelated with 
a particular field value. 
As an example let's say that our observed evidence consists
of $\evidence_{name} = \textsc{Fran Allen}$ and  
$\evidence_{occupation} = \textsc{Computer Scientist}$
but we did not know the value of the gender field, 
$\evidence_{gender} = \textsc{Missing} $. If our dataset over 
represents men (a known bias in Wikipedia), 
the sequence-to-sequence based generator is 
likely to fall back to the most prevalent patterns in the dataset and use
the masculine pronoun during generation. In turn, 
the gender field recognizer is likely
to key in on pronoun usage as a discriminative feature and predict male.
If we train the faithful generator to produce utterances that result in
maximum uncertainty in the gender 
recognizer then it is likely to avoid gendered pronouns and minimize
the chances of implying incorrect knowledge.
